Performance for the masses: Experiments with A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2016-02-03 GECCO/volunteer-clouds-gecco16.tex
Introduction has been reviewed

%Mario: Rewrote: 
%One of the aspects that must be taken into account in volunteer based
%frameworks is its {\em social} aspect in the design, with 
In general, several volunteers will be needed to
overcome the overhead involved in using a client-server architecture
and this number of volunteers is obviously not guaranteed. Therefore, the {\em social} aspect must be taken into account when designing 
volunteer based frameworks, with 
issues related to security, trust, and privacy among others. 
The computing system becomes then a {\em techno-social system}
\cite{vespignani2009predicting}, in the sense that its social aspects
cannot be separated from its technical specifications, with one
feeding into the other. One of these aspects is safety for the user running it, as well as for the scientist: the user must be reasonably sure that the
experiment is not misusing their resources and the scientist must have a
certain safety in the sense that their server is not going to be
attacked via cheating or denial of service attacks. We have decided to
approach this in a pragmatic way. Including many security features % (Paloma) I'm kind of lost here... Sentences seem to be unconnected and unrelated...
would decrease performance; on the other hand, we publish all data
resulting from the experiment once private information, such as IPs,
has been processed to an untraceable hash. The experiments themselves
are a proof that there are enough users trusting the experiment to
give it its CPU time and that there has been no attempt to cheat by
sending specially crafted chromosomes or to attack the server to make
it stop working because there was no incentive in doing so. The
system, besides, is running in a dedicated Platform as a Service (PaaS)
container or Virtual Private Server so accessing the server would only
show the few data obtained from the experiment, nothing more. Making it
free software ensured this was known by anyone in the experiment, via
links in the web page that hosted it.

In this paper, we will carry out three experiments, after establishing
the baseline of the performance that can be expected in a JavaScript
based system and its comparison with other languages in
\cite{2016arXiv160101607Manom}. First, several experiments are performed using a PaaS, and a simple Ajax client that does not
restart when a solution is found. Second, we change the client a bit so that it uses web workers, that is, it runs in the background process and it restarts. Third, we use the same
% Pablo: it restarts when the solution is found (it has not been mentioned yet)
client, but with a harder problem that cannot be easily solved by a single
volunteer and thus needs the contribution of many volunteers to
proceed. 
%Mario: refrased: 
%With these three experiments we want mainly to try and model
With these three experiments our main objective is to try and model
the behavior of users and learn how different problems and implementation choices have an influence on it.

>>>>

%Mario: Rewrote: 
%One of the aspects that must be taken into account in volunteer based
%frameworks is its {\em social} aspect in the design, with 
In general, several volunteers will be needed to
overcome the overhead involved in using a client-server architecture
and this number of volunteers is obviously not guaranteed. Therefore, the {\em social} aspect must be taken into account when designing 
volunteer based frameworks, with 
issues related to security, trust, and privacy among others. 
The computing system becomes then a {\em techno-social system}
\cite{vespignani2009predicting}, in the sense that its social aspects
cannot be separated from its technical specifications, with one
feeding into the other. One of these aspects is safety for the user running it, as well as for the scientist: the user must be reasonably sure that the
experiment is not misusing their resources and the scientist must have a
certain safety in the sense that their server is not going to be
attacked via cheating or denial of service attacks. We have decided to
approach this in a pragmatic way. Including many security features % (Paloma) I'm kind of lost here... Sentences seem to be unconnected and unrelated...
would decrease performance; on the other hand, we publish all data
resulting from the experiment once private information, such as IPs,
has been processed to an untraceable hash. The experiments themselves
are a proof that there are enough users trusting the experiment to
give it their CPU time and that there has been no attempt to cheat by
sending specially crafted chromosomes or to attack the server to make
it stop working because there was no incentive in doing so.
% (Paloma) Is this really true? Can we really state that there were no attacks because there was no incentive? Attackers don't always need an incentive to perform an attack, or the incentive could not be perceived by us. And why do the experiments prove this? Are there specific measures?
The
system, besides, is running in a dedicated Platform as a Service (PaaS)
container or Virtual Private Server so accessing the server would only
show the few data obtained from the experiment, adding security against attackers. In addition, making it
free software ensured this was known by anyone in the experiment, via
links in the web page that hosted it. % (Paloma) What was known? The fact that it was running in a PaaS? Why was that known by links?

In this paper, we will carry out three experiments, after establishing
the baseline of the performance that can be expected in a JavaScript
based system and its comparison with other languages in
\cite{2016arXiv160101607Manom}. First, several experiments are performed using a PaaS, and a simple Ajax client that does not
restart when a solution is found. Second, we change the client a bit so that it uses web workers, that is, it runs in the background process and then it restarts. Third, we use the same
% Pablo: it restarts when the solution is found (it has not been mentioned yet)
client, but with a harder problem that cannot be easily solved by a single
volunteer and thus needs the contribution of many volunteers to
proceed. 
%Mario: refrased: 
%With these three experiments we want mainly to try and model
With these three experiments our main objective is to try and model
the behavior of users and learn how different problems and implementation choices have an influence on it.
